### 2019-12-11 README.Rmd
Add dohnuts, cc @mtennekes
Make sq_dohnut more efficient

```{r}
q = sq_quadrat(sq_study_region, 4) # break into 4
plot(q)
```

>>>>

```{r}
x = sq_study_region
q = sq_quadrat(x, 4) # break into 4
plot(q)
```

Or dohnuts

```{r}
plot(sq_dohnut(x, n = 4))
dohnut_4km = sq_dohnut(x, d = 4)
dohnut_4km
plot(sf::st_geometry(dohnut_4km))
plot(dohnut_4km[3, ], col = "blue", add = TRUE)
```
